---
title: "BigMac"
author: "Adreanna Morales"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introdcution
Get an estimated demand curve for BigMacs
```{r}
BigMacData = read.csv('BigMac.csv')
attach(BigMacData)
```


plot the data
```{r}
plot(demand, price)
```
x axis = demand
y axis = price

fit a demand line to these data

```{r}
priceOne= 4.95
model1 = lm(price~demand)
summary(model1)
plot(demand, price)
abline(model1)
abline (h = priceOne, col='red')
```



price elasticity is the % change in quantity demanded divided by the % change in price elasticity

marginal revenue of any product is the dadditional revenue for saless of one additional Big Mac

Marginal Revenue is related to price elasticity by 

MR = price * (1 = elasticity)/elasticity)

Mickey D's MR = MC

E = slope of demand at price p * (price/quantity)

```{r}
slope = model1$coefficients[2]
intercept =model1$coefficients[1]
demanded = (priceOne- intercept)/slope

E = slope*priceOne/demanded

MR = priceOne * ((1+E)/E)

print(paste('price =', priceOne))
print(paste('MR = ', round(MR, 2)))
print(paste('elasticity =', round(E, 2)))
print(paste('MR = ', round(MR, 2)))

```
Slope
y = mx + b

abs = absolute value

MR = $1.41/Big Mac, they make $1.41 for every Big Mac made.

Adding round gets rid of the many numbers after the decimal place.

Profit for Big Mac:

Profit = price - cost = 4.5- MC 

```{r}
profit = priceOne - MR
print(paste('profit = ', profit))
```

